`flippant` --- An `R` package for the automated analysis of

### 2016-07-24 inst/manuscript/manuscript.rmd
typo fix

Results from `flippant`--driven analysis track prior manual analysis well. 
Deviations observed may stem from algorithmic differences such as the fitting 
routine used (`flippant` uses the the Marquardt nonlinear least squares
algorithm as implemented by @elzhov_minpack.lm:_2015) and 
general handling of significant digits and rounding. Another potential source
of minor divergence is the algorithmic *versus* manual determination of the time
point at which reductant is added in an experiment, potentialy resulting in
slightly differing determination of relative fluorescence reduction.

>>>>

Results from `flippant`--driven analysis track prior manual analysis well. 
Deviations observed may stem from algorithmic differences such as the fitting 
routine used (`flippant` uses the the Marquardt nonlinear least squares
algorithm as implemented by @elzhov_minpack.lm:_2015) and 
general handling of significant digits and rounding. Another potential source
of minor divergence is the algorithmic *versus* manual determination of the time
point at which reductant is added in an experiment, potentially resulting in
slightly differing determination of relative fluorescence reduction.
